Using Probabilistic Knockoffs of Binary Variables to Control the False Discovery Rate

### 2015-07-29 masters_paper/presentation.tex
Edited presentation 2

\begin{frame}{Knockoff Features}
    Knockoff variables can be used to control FDR in linear regression. 
    \begin{itemize}
        \item The idea is to create a forgery of each variable; if the forgeries seem about as good predictors as the originals, the originals are lousy predictors.
        \item For each variable $X_i$, create a knockoff feature $\tilde X_i$ such that, where $X^TX=G$, $\diag{X^T X} - s$ and 
            \[ \tilde X^T \tilde X = G \quad \& \quad X^T \tilde X = G - \diag{\mathbf s} \]
        \item For $\tilde X$ to exist, it must be the case that
            \[ G_L =[X\; \tilde X]^T[X\; \tilde X] = \left[ \begin{array}{cc} G & G - \diag{\mathbf s} \\ G - \diag{\mathbf s} & G \end{array}\right] \succeq 0 \]
        \item $\tilde X_i$ and $X_i$ will have same correlation with other variables, but only low correlation with each other.
        \item Given $\mathbf s$, $\tilde X$ can be generated via a rotation of $X$.
    \end{itemize}
\end{frame}

@@

\begin{frame}{Random Binary Knockoffs}
    \begin{itemize}
        \item Integer programing is NP-hard, making finding $\tilde X\in\{0,1\}^{n\times p}$ to fit correlations exactly difficult. 
        \item Instead, introduce a relaxed problem where $\tilde X\st X$ is drawn randomly such that, where $\Sigma=\cov(\mathbf x)$
            \[ \cov(\mathbf{\tilde x}, \mathbf x) = \Sigma - \diag{\mathbf s} \quad \& \quad \cov(\mathbf{\tilde x}) = \Sigma \]
        \item For this to correspond to a random binary vector, must be the case
            \[ \Sigma_L =\cov([\,\mathbf x\,\mathbf{\tilde x}\,]) = \left[ \begin{array}{cc} \Sigma & \Sigma - \diag{\mathbf s} \\ \Sigma - \diag{\mathbf s} & \Sigma \end{array}\right] \succeq 0 \]
        \item Almost same correlation condition as before, but only holds in expectation.
        \item Switch from Gramian matrix to correlation matrix makes moment condition less likely to be violated. 
    \end{itemize}
\end{frame}

\begin{frame}{Quadratic Programing}
    \begin{itemize} 
        \item Simplest approach to Random Binary Knockoffs is to draw the entries of $\tilde X$ independently based on probabilities $P\in[0,1]^{n\times p}$.
        \item $P$ should satisfy 
            \begin{center}
                \begin{tabular}{r l}
                    minimize     & $\|X^TP-(M-\diag{s})\|_{fro}^2 + \sum_{i\neq j}(P_i^T P_j - M_{ij})^2 $\\
                    subject to   & $ \mathbf 1^T P = \mathbf m $ \\
                                 & $0 \leq P \leq 1$
                \end{tabular} 
            \end{center}
        \item Can be formulated as a quadratic program with slack variables
            \begin{center}
                \begin{tabular}{r l}
                    minimize     & $\|W\|_{fro}^2 + \|V\|_{fro}^2 $ \\
                    subject to   & $ -W \leq X^TP-(M-\diag{s})\leq W $ \\
                                 & $ -V_{ij} \leq P_i^T P_j - M_{ij} \leq V_{ij} \quad \forall i\neq j$ \\
                                 & $ \mathbf 1^T P = \mathbf m $ \\
                                 & $0 \leq P \leq 1$
                \end{tabular} 
            \end{center}
        \item Huge optimization problem, likely computationally difficult.
    \end{itemize}
\end{frame}

>>>>

\begin{frame}{Knockoff Features}
    Knockoff variables can be used to control FDR in linear regression. 
    \begin{itemize}
        \item The idea is to create a forgery of each variable; if the forgeries seem about as good predictors as the originals, the originals are lousy predictors.
        \item For each variable $X_i$, create a knockoff feature $\tilde X_i$ such that, where $X^TX=G$, $\diag{X^T X} - s$ is small and 
            \[ \tilde X^T \tilde X = G \quad \& \quad X^T \tilde X = G - \diag{\mathbf s} \]
        \item $\tilde X_i$ and $X_i$ will have same correlation with other variables, but only low correlation with each other.
        \item For $\tilde X$ to exist, it must be the case that
            \[ G_L =[X\; \tilde X]^T[X\; \tilde X] = \left[ \begin{array}{cc} G & G - \diag{\mathbf s} \\ G - \diag{\mathbf s} & G \end{array}\right] \succeq 0 \]
        \item Given $\mathbf s$, $\tilde X$ can be generated via a rotation of $X$.
    \end{itemize}
\end{frame}

@@

\begin{frame}{Random Binary Knockoffs}
    \begin{itemize}
        \item Integer programing is NP-hard, making finding $\tilde X\in\{0,1\}^{n\times p}$ to fit correlations optimally difficult. 
        \item Instead, introduce a relaxed problem where $\tilde X\st X$ is drawn randomly such that, where $\Sigma=\cov(\mathbf x)$
            \[ \cov(\mathbf{\tilde x}, \mathbf x) = \Sigma - \diag{\mathbf s} \quad \& \quad \cov(\mathbf{\tilde x}) = \Sigma \]
        \item For this to correspond to a random binary vector, must be the case
            \[ \Sigma_L =\cov([\,\mathbf x\,\mathbf{\tilde x}\,]) = \left[ \begin{array}{cc} \Sigma & \Sigma - \diag{\mathbf s} \\ \Sigma - \diag{\mathbf s} & \Sigma \end{array}\right] \succeq 0 \]
        \item Almost same correlation condition as before, but only holds in expectation.
        \item Switch from Gramian matrix to correlation matrix makes moment condition less likely to be violated. 
    \end{itemize}
\end{frame}

\begin{frame}{Quadratic Programing}
    \begin{itemize} 
        \item Simplest approach to is to draw the entries of $\tilde X$ independently based on probabilities $P\in[0,1]^{n\times p}$.
        \item $P$ should satisfy 
            \begin{center}
                \begin{tabular}{r l}
                    minimize     & $\|X^TP-(M-\diag{s})\|_{fro}^2 + \sum_{i\neq j}(P_i^T P_j - M_{ij})^2 $\\
                    subject to   & $ \mathbf 1^T P = \mathbf m $ \\
                                 & $0 \leq P \leq 1$
                \end{tabular} 
            \end{center}
        \item Can be formulated as a quadratic program with slack variables
            \begin{center}
                \begin{tabular}{r l}
                    minimize     & $\|W\|_{fro}^2 + \|V\|_{fro}^2 $ \\
                    subject to   & $ -W \leq X^TP-(M-\diag{s})\leq W $ \\
                                 & $ -V_{ij} \leq P_i^T P_j - M_{ij} \leq V_{ij} \quad \forall i\neq j$ \\
                                 & $ \mathbf 1^T P = \mathbf m $ \\
                                 & $0 \leq P \leq 1$
                \end{tabular} 
            \end{center}
        \item Huge optimization problem, likely computationally difficult.
    \end{itemize}
\end{frame}
